H~1~: Branding

### 2023-08-28 notebook/results-branding.qmd
Add H2 and H3

@@

### Estimand

@@

```{r plot-h1-mm-amce, fig.width=10, fig.height=4, out.width="100%"}
#| column: page-inset-right
p_h1_mms <- h1_mms %>% 
  ggplot(aes(x = avg, y = feat_org, fill = feat_org)) +
  stat_halfeye() +
  scale_x_continuous(labels = label_percent()) +
  scale_y_discrete(labels = label_wrap(10)) +
  scale_fill_manual(values = clrs$prism[c(1, 3, 5, 7)], guide = "none") +
  labs(
    x = "Overall average predicted probability",
    y = NULL,
    fill = NULL,
    title = "Estimated marginal means"
  )

@@

```{r table-h1-mm-amce}
#| column: page-inset-right
h1_tbl_mm <- h1_mms %>% 
  group_by(feat_org) %>% 
  median_qi() %>% 
  mutate(nice = glue("{fmt_decimal(avg)}<br>{build_ci(.lower, .upper)}")) %>% 
  arrange(desc(feat_org)) %>% 
  select(feat_org, nice)

>>>>

# H~1~: Branding

@@

## Estimand

@@

```{r plot-h1-mm-amce, fig.width=10, fig.height=4, out.width="100%"}
#| column: body-outset-right
p_h1_mms <- h1_mms %>% 
  ggplot(aes(x = avg, y = feat_org, fill = feat_org)) +
  stat_halfeye() +
  scale_x_continuous(labels = label_percent()) +
  scale_y_discrete(labels = label_wrap(10)) +
  scale_fill_manual(values = clrs$prism[c(1, 3, 5, 7)], guide = "none") +
  labs(
    x = "Overall average predicted probability",
    y = NULL,
    fill = NULL,
    title = "Estimated marginal means"
  )

@@

```{r table-h1-mm-amce}
#| column: body-outset-right
h1_tbl_mm <- h1_mms %>% 
  group_by(feat_org) %>% 
  median_qi() %>% 
  mutate(nice = glue("{fmt_decimal(avg)}<br>{build_ci(.lower, .upper)}")) %>% 
  arrange(desc(feat_org)) %>% 
  select(feat_org, nice)
